---
title: "CCT Preprocessing Test"
date:"21/03/2022"
output: html_document
---
## CCT RMarkdown (February 24, 2022; Version 0.1)

This is an RMarkdown to allow for reproducible and accurate preprocessing of the CCT Psychopy 
task data created by Michael Colwell (michael.colwell@psych.ox.ac.uk / ORCID 0000-0001-7846-2879).

The task materials and preprocessing script are offered free of charge for researchers. **It is requested that researchers who publish data using these materials (task or preprocessing script) cite the code for the task
in relevant publications**. Our reference is:

[TO BE COMPLETED]

##Required R packages

You will need the following packages installed and loaded before executing the below code chunks. 

```{r libraries, echo=FALSE, include=FALSE}
library(dplyr)
library(tidyverse)
library(gtools)
library(knitr)
library(stringr)
library(purrr)
library(readxl)
library(data.table)
library(openxlsx)
library(ggpubr)
library(rstatix)
library('ez')
library(ggsignif)
library(RColorBrewer)
library(emmeans)
library(plotrix)
```

##Begin preprocessing: Setting directory, merging files and deleting unnecessary columns

You will first need to point to the directory of your task files, typically in the 'data' subfolder where the
psychopy task is located. **Please edit the path directory below after the setwd function.**

The next lines in the chunk of code will allow you to merge all data files (.csv) in the directory assigned above to a dataframe, and then delete extraneous columns from the dataframe.

**Potential error**: "Error in rbind(deparse.level, ...) : numbers of columns of arguments do not match"
**Solution**: One of the .csv files may not have run beyond the practice section, therefore not enough columns
have generated. Delete this file and then continue.

```{r b0, echo=FALSE, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls()) # clear the workspace

setwd("E:/Behavioural Tasks/2 Colour Change Detection Task - Oxford PERL/pilot_data")

CCT_files <- list.files(pattern=glob2rx("*Colour*.csv")) #create a list of files containing the word 'Back'.

CCT <- CCT_files %>% map_dfr(read.csv) #stack the files containing the word 'Back' on top of each other.

CCT <- CCT %>% rename(Participant.ID=participant) 

CCT <- CCT %>% dplyr::select(Participant.ID, ï..CondFile, mouse.clicked_name, mouse_2.clicked_name, Corr_Wedge)
                                   
#Note that the 'correctness'; column refers to the actual key they should have pressed for the actual trials and that 'correctnessP' refers to the actual key they should have pressed for the practice trials.


```
##Further parsing the dataframe 

The following chunks will allow you to further parse the data, including generating omission/comission error checks
based on conditions set in the file.

```{r b0, echo=FALSE, include=TRUE}

CCT <- CCT[!is.na(CCT$mouse.clicked_name), ]
CCT <- CCT[!(CCT$mouse.clicked_name == ""), ]

CCT_first_tidy <-CCT %>%  mutate(block = case_when((ï..CondFile == "Conditions/3_square_trial.xlsx") ~ '3_square', (ï..CondFile == "Conditions/4_square_trial.xlsx") ~ '4_square', (ï..CondFile == 'Conditions/5_square_trial.xlsx') ~ '5_square', (ï..CondFile == 'Conditions/6_square_trial.xlsx') ~ '6_square'))

CCT_first_tidy <- CCT_first_tidy %>% mutate(Loc_corr = case_when((mouse.clicked_name == "Target_2") ~ '1', TRUE ~ '0'))
         
CCT_first_tidy <- CCT_first_tidy %>% mutate(Color_corr = case_when((mouse_2.clicked_name == Corr_Wedge) ~ '1', TRUE ~ '0'))

CCT_first_tidy$Loc_corr <- as.numeric(CCT_first_tidy$Loc_corr)
CCT_first_tidy$Color_corr <- as.numeric(CCT_first_tidy$Color_corr)
         
CCT_Summary_Table <- CCT_first_tidy %>%
 group_by(Participant.ID, block) %>%
 summarize(Location_correct = sum(Loc_corr, na.rm = TRUE), 
           Colour_correct = sum(Color_corr, na.rm = TRUE))

CCT_Summary_Table2 <- CCT_first_tidy %>%
 group_by(block) %>%
 summarize(Location_correct = sum(Loc_corr, na.rm = TRUE), 
           Colour_correct = sum(Color_corr, na.rm = TRUE))

#
CCT_Summary_Table %>%
  group_by(block) %>%
  get_summary_stats(Location_correct, type = "mean_sd")


CCT_Summary_Table %>%
  group_by(block) %>%
  get_summary_stats(Colour_correct, type = "mean_sd")





CCT_Summary_Table %>%
  group_by(Block,Letter_reward) %>%
  get_summary_stats(left_TRUE_acc, type = "mean_sd")

CCT_Summary_Table %>%
  group_by(Block,Letter_reward) %>%
  get_summary_stats(mean_RT, type = "mean_sd")

#
p<-ggplot(CCT_Summary_Table, aes(x=right_TRUE_acc)) + 
  geom_histogram(color="black", fill="white")
p


Figure1 <- CCT_Summary_Table %>% 
  group_by(Block,Letter_reward) %>% ggplot(aes(x=right_TRUE_acc, color=Letter_reward))+
    geom_histogram(fill="white")+
      facet_wrap(~fct_rev(Block),nrow=1)



Figure1 <- CCT_Summary_Table %>% 
  group_by(Block,Letter_reward) %>% ggplot(aes(x=mean_RT, color=Letter_reward))+
    geom_histogram(fill="white")+
      facet_wrap(~fct_rev(Block),nrow=1)


```
