---
title: "Change_Detection_Task_Prepr_and_Analysis"
author: "Michael Colwell"
date: "2024-04-09"
output: html_document
---

#This is the preprocessing and analysis script designed for the 'Partial Change Detection Task' by Michael Colwell (michaelcolwell92@gmail.com / michael.colwell@psych.ox.ac.uk) which can be accessed here: https://github.com/mjcolwell/change_detection_task_oxford

#The task takes the raw input from psychopy (.csv files) and processes them a report that is easy to analyse. If you use this task and/or
#this script, please cite the following repository:

#Colwell, Michael, Murphy, Susannah, & Harmer, Catherine. (2023). Colour Change Detection Task (Oxford, PERL) (Psychopy). Zenodo. #https://doi.org/10.5281/zenodo.8003373

#

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library chunk

```{r cars}
library(dplyr)
library(tidyverse)
library(gtools)
library(knitr)
library(data.table)
library(ggrepel)
library(ggpubr)
library(rstatix)
library("ez")
library(ggsignif)
library(RColorBrewer)
library(emmeans)
library(plotrix)
library(lme4)
library(stringr)
library(ggplot2)
library(effectsize)
library(lmerTest)
library(cowplot)
```

## Preprocessing chunk

```{r pressure, echo=FALSE}

#Set working directory, create a list of relevant data files and merge them

setwd("C:/Users/micha/Desktop/PEACE_Behavioural_Data/Change_Detection_Task")

CDT_files <- list.files(pattern = glob2rx("*Change*.csv")) # create a list of files containing the word 'Back'.

CDT_Main <- CDT_files %>% 
  map_dfr(~ read.csv(.x, stringsAsFactors = FALSE, colClasses = c(key_resp.keys = "character")))

#Clean up Participant.ID column

CDT_Main <- CDT_Main %>% rename(Participant.ID = participant)

CDT_Main$Participant.ID <- toupper(CDT_Main$Participant.ID)

#Remove extraneous columns

CDT_Main <- CDT_Main %>% dplyr::select(Participant.ID, CondFile, Trial, Corr_Wedge, mouse.clicked_name, time_LocalisationBegin, time_LocalisationEnd, mouse_2.clicked_name, time_ColourSelectStart, time_ColourSelectEnd, frameRate) 

#Retrieve trial_type factor from the 'condition' file column (CondFile). Each trial type also doubles as 'block' as there is only one block per each trial type.

CDT_Main <- CDT_Main %>%
  mutate(Trial_Type = case_when(
    grepl("3_square", CondFile) ~ "3_Squares",
    grepl("4_square", CondFile) ~ "4_Squares",
    grepl("5_square", CondFile) ~ "5_Squares",
    grepl("6_square", CondFile) ~ "6_Squares",
    TRUE ~ NA_character_
  ))

#Remove rows where there is no 'Trial' as these will be instructions and are not relevant to analysis

CDT_Main <- CDT_Main %>% 
  filter(!is.na(Trial))

#Create 'correctness' column for spatial choices (selecting the correct square which changed).

CDT_Main <- CDT_Main %>%
  mutate(Spatial.Correct = ifelse(grepl("Target", mouse.clicked_name), 1, 0))

#Create 'correctness' column for colour choices (selecting the correct colour which changed on the colour wheel.)

CDT_Main <- CDT_Main %>%
  mutate(Colour.Correct = ifelse(mouse_2.clicked_name == Corr_Wedge, 1, 0))

#Create an 'RT' column for spatial selections.

CDT_Main <- CDT_Main %>%
  mutate(Spatial.RT.local = time_LocalisationEnd - time_LocalisationBegin)

#Create an 'RT' column for colour wheel selections.

CDT_Main <- CDT_Main %>%
  mutate(Colour.RT.local = time_ColourSelectEnd - time_ColourSelectStart)

#Convert time units in both RT columns to ms

CDT_Main <- CDT_Main %>%
  mutate(Spatial.RT.local = Spatial.RT.local * 1000)

CDT_Main <- CDT_Main %>%
  mutate(Colour.RT.local = Colour.RT.local * 1000)

#Remove all extraneous reference columns

CDT_Main <- CDT_Main %>% dplyr::select(Participant.ID, Trial, Trial_Type, Spatial.Correct, Spatial.RT.local, Colour.Correct, Colour.RT.local, frameRate)

```

```{r pressure, echo=FALSE}
#Create summary file

#Note that all accuracy values are expressed as percentages for ease of interpretation

CDT_Main_Summary <- CDT_Main %>%
  group_by(Participant.ID, Trial_Type) %>%
  summarize(Spatial.Accuracy = (sum(Spatial.Correct, na.rm = TRUE)/16)*100, 
            Colour.Accuracy = (sum(Colour.Correct, na.rm = TRUE)/16)*100,
            Spatial.RT = mean(Spatial.RT.local, na.rm = TRUE),
            Colour.RT = mean(Colour.RT.local, na.rm = TRUE))

```
```{r pressure, echo=FALSE}
#Quality checks

# Function to detect outliers
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 3.0 * IQR(x) | x > quantile(x, 0.75) + 3.0 * IQR(x))
}

#Spatial Accuracy outliers

Spatial_Accuracy_Plot <- ggplot(CDT_Main_Summary, aes(x = as.factor(Trial_Type), y = Spatial.Accuracy)) +
  geom_boxplot(outlier.shape = NA) +  # Hide outlier points in boxplot
  geom_point(data = CDT_Main_Summary[is_outlier(CDT_Main_Summary$Spatial.Accuracy), ], aes(color = Participant.ID)) + 
  geom_text_repel(data = CDT_Main_Summary[is_outlier(CDT_Main_Summary$Spatial.Accuracy), ], aes(label = Participant.ID), color = "black", size = 3) +  # Label outliers
  labs(title = "",
       y = "\nAccuracy for spatial location (%)\n",
       x = "\nTrial Type\n") +
  theme_minimal()+
  theme(text = element_text(size = 16))

#Colour Accuracy outliers

Colour_Accuracy_Plot <- ggplot(CDT_Main_Summary, aes(x = as.factor(Trial_Type), y = Colour.Accuracy)) +
  geom_boxplot(outlier.shape = NA) +  # Hide outlier points in boxplot
  geom_point(data = CDT_Main_Summary[is_outlier(CDT_Main_Summary$Colour.Accuracy), ], aes(color = Participant.ID)) + 
  geom_text_repel(data = CDT_Main_Summary[is_outlier(CDT_Main_Summary$Colour.Accuracy), ], aes(label = Participant.ID), color = "black", size = 3) +  # Label outliers
  labs(title = "",
       y = "\nAccuracy for colour (%)\n",
       x = "\nTrial Type\n") +
  theme_minimal()+
  theme(text = element_text(size = 16))

#Spatial localisation

Spatial_Localisation_Plot <- ggplot(CDT_Main_Summary, aes(x = as.factor(Trial_Type), y = Spatial.RT)) +
  geom_boxplot(outlier.shape = NA) +  # Hide outlier points in boxplot
  geom_point(data = CDT_Main_Summary[is_outlier(CDT_Main_Summary$Spatial.RT), ], aes(color = Participant.ID)) +
  geom_text_repel(data = CDT_Main_Summary[is_outlier(CDT_Main_Summary$Spatial.RT), ], aes(label = Participant.ID), color = "black", size = 3) +  # Label outliers
  labs(title = "",
       y = "\nSpatial Localisation Time (ms)\n",
       x = "\nTrial Type\n") +
  theme_minimal()+
  theme(text = element_text(size = 16))

#Colour localisation

Colour_Localisation_Plot <- ggplot(CDT_Main_Summary, aes(x = as.factor(Trial_Type), y = Colour.RT)) +
  geom_boxplot(outlier.shape = NA) +  # Hide outlier points in boxplot
  geom_point(data = CDT_Main_Summary[is_outlier(CDT_Main_Summary$Colour.RT), ], aes(color = Participant.ID)) + 
  geom_text_repel(data = CDT_Main_Summary[is_outlier(CDT_Main_Summary$Colour.RT), ], aes(label = Participant.ID), color = "black", size = 3) +  # Label outliers
  labs(title = "",
       y = "\nColour Localisation Time (ms)\n",
       x = "\nTrial Type\n") +
  theme_minimal()+
  theme(text = element_text(size = 16))

########################################


````

```{r pressure, echo=FALSE}
#Removing excluded data & merging demographics file

#Removal of excluded data:

#No consistent outlier across dataset - no removals

#removal_df <- subset(CDT_Main_Summary, Participant.ID != "P003")

#CDT_Main_Summary <- droplevels(removal_df)

#Adding demographics file

setwd("C:/Users/micha/Desktop/PEACE_Behavioural_Data/Allocation_and_Demographics")

Allocation_and_Demographics <- read.csv("Allocation_And_Demo.csv")

Allocation_and_Demographics$Participant.ID <- as.factor(Allocation_and_Demographics$Participant.ID)

CDT_Full <- merge(CDT_Main_Summary, Allocation_and_Demographics, by = "Participant.ID")

````
```{r pressure, echo=FALSE}
#Inferential analyses

#Spatial Accuracy analysis

Spatial_Accuracy_Model <- aov(Spatial.Accuracy ~ Allocation + Trial_Type + + Allocation:Trial_Type + Error(Participant.ID), data = CDT_Full)

summary(Spatial_Accuracy_Model)

# Calculate estimated marginal means (EMMs) for Allocation*Condition interaction
model_linear <- lmer(Spatial.Accuracy ~ Allocation + Trial_Type + Allocation:Trial_Type + (1 | Participant.ID), data = CDT_Full)

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation | Trial_Type)

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

CDT_Full %>%
  group_by(Trial_Type, Allocation) %>%
  get_summary_stats(Spatial.Accuracy, type = "mean_sd")

############################################################

#Colour Accuracy analysis

Spatial_Accuracy_Model <- aov(Colour.Accuracy ~ Allocation + Trial_Type + Allocation:Trial_Type + Error(Participant.ID), data = CDT_Full)

summary(Spatial_Accuracy_Model)

# Calculate estimated marginal means (EMMs) for Allocation*Condition interaction
model_linear <- lmer(Colour.Accuracy ~ Allocation + Trial_Type + Allocation:Trial_Type + (1 | Participant.ID), data = CDT_Full)

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation | Trial_Type)

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

CDT_Full %>%
  group_by(Trial_Type, Allocation) %>%
  get_summary_stats(Colour.Accuracy, type = "mean_sd")

#################################################################

#Spatial Localisation (RT) analysis 

Spatial_RT_Model <- aov(Spatial.RT ~ Allocation + Trial_Type + + Allocation:Trial_Type + Error(Participant.ID), data = CDT_Full)

summary(Spatial_RT_Model)

# Calculate estimated marginal means (EMMs) for Allocation*Condition interaction
model_linear <- lmer(Spatial.RT ~ Allocation + Trial_Type + Allocation:Trial_Type + (1 | Participant.ID), data = CDT_Full)

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

#No effect

#Colour localisation (RT) analysis

Colour_RT_model <- aov(Colour.RT ~ Allocation + Trial_Type + + Allocation:Trial_Type + Error(Participant.ID), data = CDT_Full)

summary(Colour_RT_model)

# Calculate estimated marginal means (EMMs) for Allocation*Condition interaction
model_linear <- lmer(Colour.RT ~ Allocation + Trial_Type + Allocation:Trial_Type + (1 | Participant.ID), data = CDT_Full)

eta_squared(model_linear, ci = 0.95, alternative = "two.sided")

EMM_2 <- emmeans(model_linear, ~ Allocation | Trial_Type)

# Calculate pairwise comparisons for the specified contrasts
pairwise_comparisons <- pairs(EMM_2, adjust = "holm")

summary(pairwise_comparisons)

effect_size <- eff_size(EMM_2, sigma = sigma(model_linear), edf = df.residual(model_linear))

summary(effect_size)

CDT_Full %>%
  group_by(Trial_Type, Allocation) %>%
  get_summary_stats(Colour.RT, type = "mean_sd")

#####

````


